Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-17 doc/main_jfm.tex
new Figure 8

\subsection{Stretching and Permeability}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}
Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
that vanishes as the configuration tends toward the equilibrium state.  
This suggests that the initial collection of JP is under tension and
this tension is relaxed as fluid is expelled through the inter-particle
spacing. To make a comparison with membrane continuum mechanics, lipid
bilayer membranes have a large area modulus $K_A$ of about $240$ pN
nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
non-tensed state. In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. A stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R$ is the radius of the circular vesicle. The factor
$R^{-1}$ is the total curvature since the principle curvature in the
direction of the cylinder is zero.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
%\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
%\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

>>>>

\subsection{Stretching and Permeability}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}

\begin{figure}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
that vanishes as the configuration tends toward the equilibrium state.  
This suggests that the initial collection of JP is under tension and
this tension is relaxed as fluid is expelled through the inter-particle
spacing. To make a comparison with membrane continuum mechanics, lipid
bilayer membranes have a large area modulus $K_A$ of about $240$ pN
nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
non-tensed state. In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. A stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R$ is the radius of the circular vesicle. The factor
$R^{-1}$ is the total curvature since the principle curvature in the
direction of the cylinder is zero.
